\huge{ \emph{Supplement to} Algorithms For Shaping a Particle Swarm\\ With a Shared Control Input Using Boundary Interaction}

### 2016-09-06 RA-L/experiment.tex

\subsection{Hardware Experiment: Position Control of n Robots}

>>>>

\subsection{Hardware Experiment: Position Control of n Robots}
The hardware setup has a bounded platform, magnetic sliders, and a magnetic guide board.  Designs for each are available at \citep{arunhardware}. The pink boundary is toothed with a white free space, as shown in Fig \ref{fig:construction2d}. Only discrete, 1 cm moves in the $x$ and $y$ directions are used. The goal configuration highlighted in the top right corner represents a `U' made of seven sliders. The dark red configuration is the current position of the sliders. 
Due to the discretized movements allowed by the boundary, drift moves follow a 1 cm square.  Free robots return to their start positions but robots on the boundary to move laterally, generating a net sliding motion.

Figure \ref{fig:construction2d} follows the motion of the sliders through iterations  $k$=1, 2 and 7. All robots receive the same control inputs, but boundary interactions breaks the control symmetry.  Robots reach their respective goal position in a first-in, first-out arrangement beginning with the bottom-left robot from the staging zone occupying the top-right position of the build zone.
